Lineage Analysis of CRISPR and shRNA Screens

### 2018-08-27 lineages_18Q3.Rmd
added metadata exploration section

@@

```{r}
crispr_data <- readRDS("./data_munging/rds/crispr_data_18Q3.rds")
crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
# write.table(crispr_data, file = "crispr_data.tsv", quote = FALSE, sep = "\t")
```

>>>>

###  Metadata exploration

```{r}
tissue_summ <- crispr_meta %>% group_by(primary_tissue) %>% tally()
disease_summ <- ccl_info %>% group_by(Primary.Disease) %>% tally()
```

```{r fig.height=5, fig.width=8}
ggplot(data = tissue_summ) + 
  aes(x = 0, y = n, fill = primary_tissue, label = primary_tissue) +
  geom_histogram(color = "black", stat = "identity") +
  geom_text(position = position_stack(vjust = 0.5))
```

@@

```{r}
crispr_data <- readRDS("./data_munging/rds/crispr_data_18Q3.rds")
crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
write.table(crispr_data[, c("Hugo_Symbol", "Broad_ID", "Score", "Primary.Disease", "primary_tissue", "Mutation_Status")], file = "~/Desktop/crispr_data_select.tsv", quote = FALSE, sep = "\t")
```
